### 2013-01-08 exercise2/paper/paper.tex
handed in

%
%
%
\section{TODO}

\begin{itemize}
\item Implementation of cutsom bn-searcher
\item documentation of cutsom bn-searcher
\item comparison and interpretation of the results
\end{itemize}

@@

@@

\todo{give a table with the results for hill climber with empty start solution as well as with naive bayes.}

@@

\todo{Insert tables containing the classification results of the iterated local search}.

@@

One can see that the iterated local search does not or in some cases just slightly perform better than the pre-implemented Hill-Climber algorithm. This is mostly due to the fact that for our test data sets the Naive Bayes representation yields the best or at least nearly the best result. The Hill climber doesn't perform many neighborhood operations. For the contraception data set there are no neighborhood operations at all and for the adult data set its just a few operations (about five operations). The perturbation normally leads to worse solutions and local search then finds a net which is close to Naive Bayes or pretty similar to it so we don't get a better solution than the solution after the local search.

%
%
%\subsection{Description}
%
%As shown in listing \ref{hcSearch}, Hill Climber calculates an optimal solution based on the current network iteratively until no opration can be found to improve the network or the new network is only slightly better than the previous one. To find the best operation all possible operations get evaluated and the best one is returned. The algorithm stops, when it finds a local optima.
%
%\begin{lstlisting}[caption={HillClimbers search algorithm},label=hcSearch]
%double fScore = calcScore(bayesNet);
%Operation oOperation = getOptimalOperation(bayesNet, instances);
%while ((oOperation != null) && (oOperation.m_fScore > fScore)) {
%	performOperation(bayesNet, instances, oOperation);
%	fScore = oOperation.m_fScore;
%	oOperation = getOptimalOperation(bayesNet, instances);
%}  
%\end{lstlisting}

%
%
%\subsection{Test Results}
%
%Two data sets are used to test the search algorithm. These are x and y from the assignment 1.
%
%\todo{insert results of test}
%
%As shown in the result listing, \todo{describe result} ....

%
%

%\subsection{Description}
%
%Like the Hill Climber, our improved search algorithm introduces an initial Naive Bayes like network where each attribute has the classification attribute as parent.
%
%Then the Hill Climber algorithm is executed to find a local optima. To find other local optima, our search algorithm iteratively selects a neighbor of the found network and uses it as initial network for the Hill Climber to hopefully find better local optima than the first one.
%
% The intial network we use in each iteration is a random neighbor of the previously found one. It does not matter if it is better or worse.
%
%If the Hill Climber finds a better network it is stored as the current best found network and if the seacher cannot find a better network after a given number of iterations, the algorithm stops and yields the best solution found.

%
%
%%
%\section{Comparison}
%
%TODO:
%* used datasets
%* accuracy results
%* runtime/performance

>>>>

@@

\newpage

@@

\begin{lstlisting}[caption={Classification result with default Hill Climber},label=listingDefault]
"ADULT DATA SET"
"Original Hill Climber classifier"
              pctCorrect             pctIncorrect          pctUnclassified 
              84.7025583               15.2974417                0.0000000 
                   kappa        meanAbsoluteError     rootMeanSquaredError 
               0.6078686                0.1722236                0.3319906 
   relativeAbsoluteError rootRelativeSquaredError 
              47.1008155               77.6450216 
\end{lstlisting}

@@

\begin{lstlisting}[caption={Classification result with iterated local search and Hill Climber},label=listingExtended]
"ADULT DATA SET"
"New iterated local search classifier"
              pctCorrect             pctIncorrect          pctUnclassified 
              84.8376893               15.1623107                0.0000000 
                   kappa        meanAbsoluteError     rootMeanSquaredError 
               0.6114594                0.1711662                0.3298876 
   relativeAbsoluteError rootRelativeSquaredError 
              46.8116196               77.1531638

\end{lstlisting}

@@

One can see that the iterated local search does improve the results slightly the pre-implemented Hill-Climber algorithm. The perturbation normally leads to worse solutions and local search then finds a net which is close to Naive Bayes or pretty similar to it so we don't get a better solution than the solution after the local search.

\begin{lstlisting}[caption={Comparison of classification results},label=listingComparison]
"Difference of details"
              pctCorrect             pctIncorrect          pctUnclassified 
             0.135130985             -0.135130985              0.000000000 
                   kappa        meanAbsoluteError     rootMeanSquaredError 
             0.003590769             -0.001057442             -0.002103060 
   relativeAbsoluteError rootRelativeSquaredError 
            -0.289195892             -0.491857758 
"Difference of confusion matrices"
       predicted
        >50K <=50K
  >50K    26   -26
  <=50K  -18    18

\end{lstlisting}
